The impact of cosmic variance on simulating weak lensing surveys

### 2015-02-27 Writeup/paper_v3.tex
Claires comments addressed

\new{
One might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
In Figs.~\ref{fig:rms_ellip}--\ref{fig:median_dvcbtt}, this does not appear to be the case. 
It is possible that a redshift bin may have an overdensity in one part of the field and an
underdense region in another. 
In such a scenario, the redshift slice might appear to be `neutral' in our histogram-based method of
finding overdensities, while still having significant large-scale structure affecting the
morphological mix of galaxies that complicates the situation. 
This indeed turns out to be the case
in the `neutral' regions of the COSMOS field.
Using X-ray information in the COSMOS field, \cite{COSMOS_XRAY} have detected several galaxy groups in the
redshift range $z=0.425-0.575$.}
\new{\cite{Kovac_Density10k} report structures that are large and extended (in RA-DEC) within this redshift range. 
%Thus, $z=0.4-0.55$ range indeed is a mixture of overdense and underdense regions. 
It is a challenge to make definitive statements regarding the relationship between environment and
morphology in neutral regions that are composed of mixtures of multiple overdense and underdense regions. 
In addition, the redshift evolution, albeit weak, can make the neutral bins look like overdense or underdense regions.
For instance, the neutral bins look overdense-like in Figs.~\ref{fig:rms_ellip}-\ref{fig:median_sersicn} but underdense-like
in Fig.~\ref{fig:median_dvcbtt}, partly due to redshift evolution.
However, when the overdensity (or underdensity) is prominent, we observe that the environment in
which a galaxy resides affects its morphology, so the appearance of the neutral bins does not
undermine the main conclusions of this paper.
}

@@

\new{The number of galaxies in overdense bins is typically higher than the number in underdense bins by about a factor of 2. (See Table ~\ref{table:GalaxyCounts}). 
To eliminate the plausibility (with great confidence) that this varying sample size is not responsible for the trend observed, we repeated our analysis with only 50 per cent of overdense galaxies that were selected randomly. 
The vertical errorbars for overdense regions get bigger due to reduced sample size, but  the
statistical significance of our conclusions is still nearly as high as in the original analysis.}

>>>>

\new{
One might expect the points corresponding to neutral regions to lie in between the points for overdense and underdense regions. 
In Figs.~\ref{fig:rms_ellip}--\ref{fig:median_dvcbtt}, this does not always appear to be the case. 
It is possible that a redshift bin may have an overdensity in one part of the field and an
underdense region in another. 
In such a scenario, the redshift slice might appear to be `neutral' in our histogram-based method of
finding overdensities, while still having significant large-scale structure affecting the
morphological mix of galaxies that complicates the situation. 
This indeed turns out to be the case
in the `neutral' regions of the COSMOS field.
Using X-ray information in the COSMOS field, \cite{COSMOS_XRAY} have detected several galaxy groups in the
redshift range $z=0.425-0.575$.}
\new{\cite{Kovac_Density10k} report structures that are large and extended (in RA-DEC) within this redshift range. 
%Thus, $z=0.4-0.55$ range indeed is a mixture of overdense and underdense regions. 
It is a challenge to make definitive statements regarding the relationship between environment and
morphology in neutral regions that are composed of mixtures of multiple overdense and underdense regions. 
In addition, the redshift evolution, albeit weak, can make the neutral bins look like overdense or underdense regions.
For instance, the neutral bins look overdense-like in Figs.~\ref{fig:rms_ellip}-\ref{fig:median_sersicn} but underdense-like
in Fig.~\ref{fig:median_dvcbtt}, partly due to redshift evolution.
However, when the overdensity (or underdensity) is prominent, we observe that the environment in
which a galaxy resides affects its morphology, so the appearance of the neutral bins does not
undermine the main conclusions of this paper.
}

@@

\new{The number of galaxies in overdense bins is typically higher than the number in underdense bins by about a factor of 2. (See Table ~\ref{table:GalaxyCounts}). 
To eliminate the possibility (with great confidence) that this varying sample size is 
responsible for the trend observed, we repeated our analysis with only 50 per cent of overdense galaxies that were selected randomly. 
The vertical errorbars for overdense regions get bigger due to reduced sample size, but  the
statistical significance of our conclusions is still nearly as high as in the original analysis.}
